\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{bbm}
\usepackage{lipsum}
\usepackage{fancyhdr}
\usepackage{calrsfs}
\usepackage{tikz-cd} 

\newtheorem{theorem}{Theorem}[section] 
\newtheorem{proposition}{Proposition}[section] 
\newtheorem{definition}{Definition}[section] 
\newtheorem{lemma}{Lemma}[section] 
\newtheorem{notation}{Notation}[section] 
\newtheorem{remark}{Remark}[section] 
\newtheorem{corollary}{Corollary}[section] 
\newtheorem{terminology}{Terminology}[section] 
\newtheorem{example}{Example}[section] 
\numberwithin{equation}{section}

\DeclareMathOperator{\diam}{diam}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Dom}{Dom}
\DeclareMathOperator{\grad}{grad}
\DeclareMathOperator{\Span}{Span}
\DeclareMathOperator{\interior}{int}
\DeclareMathOperator{\ind}{ind}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\ob}{ob}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\MaxSpec}{MaxSpec}
\DeclareMathOperator{\PreSh}{PreSh}
\DeclareMathOperator{\Sh}{Sh}
\DeclareMathOperator{\Fun}{Fun}
\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\Fr}{Fr}
\DeclareMathOperator{\Image}{Im}
\DeclareMathOperator{\Coker}{Coker}
%\newcommand*{\name}[\num_arguments][default values]{{\color{#1}\Large #2}}
\newcommand*{\multivar}[2]{{#1_1,\cdots,#1_{#2}}}
\newcommand*{\localization}[2]{#1_{\mathfrak{#2}}}
\newcommand*{\ringedspacemorph}[1]{(#1,#1^{\#})}
\newcommand*{\sheaf}[2]{(#1,{\mathcal{#2}}_{#1})}

\newcommand{\fib}[1]{%
  \mathbin{\mathop{\times}\limits_{#1}}%
}
\newcommand{\tens}[1]{%
  \mathbin{\mathop{\otimes}\limits_{#1}}%
}

\title{Algebraic Geometry 1}
\author{So Murata}
\date{2024/2025 Winter Semester - Uni Bonn}

\begin{document}
\maketitle
\subsection*{46}

Universally closedness is stable under the base change by definition. We will prove both separated and finite-type are stable under any base change.

\subsubsection*{Being of separated is stable under the base change.}

Let $f:X\to Y$ be a morphism of schemes over a base $S$. Let $S'\to S$ be a morphism of schemes. Let $f':X_{S'}\to Y_{S'}$ be the base change of $f$. Then the diagonal morphism of $f'$ is 
\begin{equation*}
\Delta_{f'}:X_{S'} = S'\fib{S}X\to X_{S'}\fib{Y_{S'}X_{S'}} = S'\fib{S}(X\fib{Y}X)
\end{equation*}
which can be seen as the base change of $\Delta_f$. Since closed immersion is stable under base change from the previous sheet. We need to show that quasi-compactness is stable under the base change.\\
\par We see that it is enough to prove the case for affine schemes. Let $Y=\Spec(B),Y'=\Spec(B')$ be affine. And let $g:X\to Y$ be quasi-compact. Then $X$ can be covered by a finite collection of affine open subschemes $\Spec(A_i)$ and then
\begin{equation*}
X'=X\fib{Y}Y'
\end{equation*}
is covered by the finite collection of affine open subschemes $\Spec(A_i\tens{B}B')$ by the definition of fiber products. Thus $X'$ is quasi-compact with $Y'$ being quasi-compact.

\subsubsection*{Being of finite type is stable under the base change.}

Let $f:X\to Y$ be of finite type and $g:S'\to S$ be a scheme morphism. 
\[
\begin{tikzcd}
X'=X\fib{S}S'\arrow[r,"f'"]\arrow[d]&S'\arrow[d,"g"]\\
X\arrow[r,"f"]&S
\end{tikzcd}
\]

Where $S=\bigcup_{i\in I} S_i,S_i = \Spec(B_i)$. We have
\begin{equation*}
f^{-1}(S_i) = \bigcup_{j\in J}U_{i_j}, U_{i_j} = \Spec(A_{i_j})
\end{equation*}
where $J$ is finite. We can regard $A_{i_j}$ as a finitely generated $B_i$ algebra.\\
\par $g^{-1}(S_i)$ is an open subscheme, thus $g^{-1}(S_i) = \bigcup_{k\in K}W_{i_k}, W_{i_k} = \Spec(C_{i_k})$. We derive that 
\begin{equation*}
S' = g^{-1}(S) = \bigcup_{i,k} W_{i_k}.
\end{equation*}
We have
\begin{equation*}
f'^{-1}(W_{i_j}) = X\fib{S}W_{i_j} = f^{-1}(S_i)\fib{S_i}W_{i_j} = \bigcup_{k\in K} U_{i_k}\fib{S_i}W_{i_j} = \bigcup_{k\in K} \Spec(A_{i_k}\tens{B_i}C_{i_j}).
\end{equation*}

Therefore each $f'^{-1}(W_{i_j})$ can be covered by finitely many affine sets. We have $A_{i_k}$ is finite over $B_i$, there are $a_1,\cdots,a_n\in A_{i_k}$ such that
\begin{equation*}
A_{i_k} = B_i[a_1,\cdots,a_n].
\end{equation*}
We also have $C_{i_j}$ is an $B_i$ algebra, thus by scalar multiplication we have
\begin{equation*}
A_{i_k}\tens{B_i}C_{i_j} = C_{i_j}[a_1\tens{B_i}1,\cdots,a_n\tens{B_i}1].
\end{equation*}
We derived that base change preserves finite type. \\
\par In conclusion, properness is stable under base changes.

\section*{Exercise 45}

First let us assume that we have $X=\Spec(A), S = \Spec(\mathbb{F}_{p})$ with the morphism $\Fr_X:X\to S$ induced by a homomorphism of rings of finite type $\varphi:\mathbb{F}_{p}\to A$. Thus $A$ is automatically of characteristic $p$. Since $\varphi$ is of finite type we have
\begin{equation*}
A = \mathbb{F}_{p}[a_1,\cdots,a_n]
\end{equation*}
for some $a_1,\cdots,a_n\in A$. Under this condition, we also have that $F_S = id$. Then 
\begin{equation*}
X^{(p)} = X\fib{S}S = \Spec(A\tens{\mathbb{F}_p}\mathbb{F}_p) = \Spec(A) = X.
\end{equation*}
And $F_{X/S}$ is an identity.\\
\par In the case where $X=\Spec(A)$ and $S=\Spec(\mathbb{F}_{p^r}$. From Commutative Algebra, we know that 
\begin{equation*}
A \cong \mathbb{F}_{p^r}[(X_i)_{i\in I}]/((f_j)_{j\in J}),
\end{equation*}
for some variables and polynomials. Then $A^{(p)}$ is such that 
\begin{equation*}
A^{(p)} \cong \mathbb{F}_{p^r}[(X_i)_{i\in I}]/((f_j^p)_{j\in J}),
\end{equation*}

And $F_{X/S}$ is induced by the inclusion from $\varphi(x) = x^p$.

\end{document}