\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{bbm}
\usepackage{lipsum}
\usepackage{fancyhdr}
\usepackage{calrsfs}
\usepackage{tikz-cd} 

\newtheorem{theorem}{Theorem}[section] 
\newtheorem{proposition}{Proposition}[section] 
\newtheorem{definition}{Definition}[section] 
\newtheorem{lemma}{Lemma}[section] 
\newtheorem{notation}{Notation}[section] 
\newtheorem{remark}{Remark}[section] 
\newtheorem{corollary}{Corollary}[section] 
\newtheorem{terminology}{Terminology}[section] 
\newtheorem{example}{Example}[section] 
\numberwithin{equation}{section}

\DeclareMathOperator{\diam}{diam}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Dom}{Dom}
\DeclareMathOperator{\grad}{grad}
\DeclareMathOperator{\Span}{Span}
\DeclareMathOperator{\interior}{int}
\DeclareMathOperator{\ind}{ind}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\ob}{ob}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\PreSh}{PreSh}
\DeclareMathOperator{\Fun}{Fun}
\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\Image}{Im}
\DeclareMathOperator{\Ad}{Ad}
\DeclareMathOperator{\ad}{ad}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\Lie}{Lie}


\title{V4A1 Sheet 5}
\author{So Murata}
\date{2024/2025 Winter Semester - Uni Bonn}

\begin{document}
\maketitle
\section*{26}

Let $\varphi:A\to\Gamma(X,\mathcal{O}_X)$ be a homomorphism of rings.\\

\par By the definition of schemes, there exists an open covering $(U_i)_{i\in I}$ of $X$ such that 
\begin{equation*}
\forall i\in I, \mathcal{O}(U_i) \cong (\Spec A_i,\mathcal{O}_{\Spec A-i})
\end{equation*}
for some ring $A_i$.\\
\par Let $\rho^{X}_{XU_i}$ be a restriction map. Then $\varphi\circ\rho_{XU_i}:\mathcal{O}_{\Spec A}(U_i)\to \mathcal{O}_X(U_i)=A_i$ is a ring homomorphism. Thus there exists a morphism of ringed spaces $(f_i,f_i^{\#}):(\Spec A_i,\mathcal{O}_{\Spec A_i})\to(\Spec A,\mathcal{O}_{\Spec A})$ corresponding to $9\varphi\circ\rho_{XU_i}$. We will show that this can be glued to a unique morphism of ringed spaces $(f,f^{\#})$.\\
\par Indeed, by construction of structure sheaves and restrictions, we have that $\{(f_i,f_i^{\#})\}_{i\in I}$ satisfies the sheaf condition. Thus can be glued to a unique morphism $(f,f^{\#})$. The correspondence $\varphi\circ\rho_{XU_i}\leftrightarrow (f_i,f_i^{\#})$ is a bijection. Therefore, $\varphi\to(f,f^{\#})$ is an injection. By the same argument to the restrictions of $(f,f^{\#})$ and the sheaf condition, we derive that this is a surjection. 

\section*{27}

\subsection*{(i)}

Let $(U_i)_{i\in I}$ be an open cover of $X$ such that 
\begin{equation*}
\mathcal{O}_X \cong \Spec A_i.
\end{equation*}
Let $\iota_i:A_i\to \tilde{A}_i$ be an inclusion. Then we can define a morphism $\nu_i:\tilde{U}_i\to U_i$ by 
\begin{equation*}
\nu_i(\mathfrak{q}) = \iota_i^{-1}(\mathfrak{q}).
\end{equation*}

By the definition of affine schemes and its restrictions, $(\nu_i)_{i\in I}$ satisfies the sheaf condition, thus there exists $\tilde{X}$ and $\nu:\tilde{X}\to X$ extending each $\nu_i$. \\
\par By the construction, $\mathcal{O}_{\tilde{X}}(\tilde{U}_i)\cong\Spec \tilde{A}_i$. Since $\tilde{A}_i$ is integrally closed, $\tilde{A}_{i,\mathfrak{p}}$ is also integrally closed for each $\mathfrak{p}\in\Spec \tilde{A}_i$. Therefore, $\tilde{X}$ is normal.

\subsection*{(ii)}

Let $U$ be a neighborhood of $x\in X$ such that $\mathcal{O}_X(U)\cong\Spec A$. Suppose $f:Z\to X$ be a dominant morphism of schemes then $f(Z)$ is dense in $X$.\\
Let $V=f^{-1}(U)$. Since $f$ is dominant, we have that the ring homomorphism induced by $f$, $\varphi: A=\mathcal{O}_X(U)\to \mathcal{O}_Z(V)=B$ is an injection. Since $A$ is an integral domain and $B$ is integrally closed, there is a unique homomorphism $\tilde{\varphi}$ such that
\begin{equation*}
\varphi = \tilde{\varphi}\circ\iota
\end{equation*}
where $\iota:A\to\tilde{A}$ is an injection and $\tilde{\varphi}:\tilde{A}\to B$. By using the previous problem, there is a morphism of scheme $(g,g^{\#}):((V,\mathcal{O}_Z|_V),(U,\Spec A))\to$ corresponding to $\tilde{\varphi}$ such that $\nu\circ g^{\#} = f^{\#}$.

\end{document}
